\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-27 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Adding modified schematics and new box and whisker plots for projections

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL
\usepackage{floatpag}
\usepackage{lipsum}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes, caption, subcaption}

@@

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{1}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1in}%
\addtolength{\topmargin}{-.8in}%

@@

	\begin{figure}[H]
		\centering
		\small
		\includegraphics[width = \textwidth]{Figs/BaseVsRecon_Emp_results.pdf}
		\caption{Difference of MSE between Base forecasts and reconciled forecasts over the replications is presented. Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
	\end{figure}

@@

	\begin{figure}
		\centering
		\begin{subfigure}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=\linewidth]{Figs/InsampDir_1.pdf}
%			\label{fig:InsampDir_1}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=\linewidth]{Figs/InsampDir_2.pdf}
%			\label{fig:InsampDir_2}
		\end{subfigure}

		\vspace{1cm}

		\begin{subfigure}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=\linewidth]{Figs/OrthProj.pdf}
%			\label{fig:OrthProj}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.5\textwidth}
			\centering
			\includegraphics[width=\linewidth]{Figs/ObliqProj.pdf}
%			\label{fig:ObliqProj}
		\end{subfigure}

%		\begin{subfigure}[t]{\textwidth}
%			\centering
%			\includegraphics[width=\linewidth]{example-image-c.pdf}
%			\caption{Price regulation} \label{fig:timing3}
%		\end{subfigure}
		\caption{A schematic to represent orthogonal and oblique reconciliation.  Points in orange colour in top left figure represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows an oblique projection.} \label{fig:OthogonalVSOblique_projection}
	\end{figure}

@@

	\textcolor{red}{GA: I will rewrite/review this when we decide where we put all our results - I am referring to the projection results - currently I think it is best that everything goes here and we make a comment at the end of Section 3.3 guiding the reader to the results here. This will make the empirical application a bit broader not only about bias correction, i.e., both about showing how projections work and how bias correction works.} Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice. Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}). However, our motivation in this study is to demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.

@@

	We use ``overnight trips'' across Australia as a measure of domestic tourism flows. The data are provided by the National Visitor Survey (NVS) and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more. Tourism flows in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers. Hence, there are $110$ series across the hierarchy with $75$ bottom-level series. More information about the series and the geographical hierarchy is presented in Table \ref{table:A1} in the Appendix. The data span the period January 1998 to December 2017, which gives a total of $240$ observations per series.

Figure \ref{fig:Total_TSplots} shows time, sub-series and seasonal plots of the total aggregate overnight trips. As is usual with tourism flows these show a strong seasonal pattern. Overnight trips peak in January corresponding to the summer vacation season in Australia. There are also some lower peaks observed in April, July and October corresponding to school holidays. On the other hand the month with the least overnight trips is February indicating that people travel least for the month following their summer vacation. The time plot shows a pronounced upward trend starting from around 2010 till the end of the sample, with the data being fairly flat from the beginning of the sample and a slight downward trend during 2004-2010.

The top panel of Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for the seven states, hence the first-level of the hierarchy. The panels below show some selected series from the second-level zones and the bottom-level regions of the geographical hierarchy. The plots display the diversity of time series features, within but also between levels. For example, noticeable at the first-level is the asynchronous seasonal pattern of the Northern Territory to the other states. For the Northern Territory the high tourist season occurs during June-August with July being the peak, while the low season is during December-February. This reflects the tropical climate of the Northern Territory, with Australians mostly visiting the North during its dry winter-season rather than the wet summer season. Noticeable as we move to the lower levels is the variation in the signal-to-noise ratio, with the regional bottom-level series being noisier compared to the series from levels above. This of course highlights the importance of modelling series at all levels without any loss of valuable information.

We should note here that we have observed an anomalous observation for `Adelaide Hills' for December-2002. We replace this observation with the average overnight trips on December-2001 and December-2003 for the same destination. \textcolor{red}{Puwasala can you please describe here how this was anomalous. I'm wondering if this is a Bali bombing effect where we had a huge spike in Australian domestic tourism because of the Bali bombings in Oct with Australians travelling within Australia due to them being scared basically.}

Starting from a training window of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$ we generate $h=1$ to $h=6$ steps-ahead forecasts. Using a rolling window we repeat the exercise until the end of the sample. This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.

	\begin{figure}
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplots.pdf}
		\caption{Total domestic overnight trips (in logs) for Australia from January 1998 to December 2017. The top-panel shows a time plot; the bottom-left panel a sub-series plot for each month; the bottom-right panel shows a seasonal plot coloured by year.} \label{fig:Total_TSplots}
	\end{figure}

	\begin{figure}
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots1.pdf}
		\caption{Time plot of overnight trips for some selected series from different disaggregate levels of the hierarchy. All values are presented in log scale. To avoid impact from the zero values we added a constant 1 to all observations}\label{fig:States_Zones_Regs_TSplots}
	\end{figure}

	\subsection{Transformations and bias adjustments}

	We first transform each series in the hierarchy using two types of transformations. Namely, we perform a log-transformation and also a more general Box-Cox transformation

\begin{equation} \label{eq:BoxCox_transformation}
	x_t =
	\begin{cases}
	\log(y_t) & \text{for log transformation} \\
	\frac{y_t^\lambda - 1}{\lambda}  & \text{for Box-Cox transformation, $\lambda \ne 0$}
	\end{cases}
\end{equation}

. Equation (\ref{eq:BoxCox_transformation}) gives the mathematical formula for these transformations. A constant (in particular $1$) is added to each series to avoid the impact of zero observations when taking log transformations, as some zeros exist in the bottom-level series.

We note here that the two sets of transformations (log and the general Box-Cox) were applied separately to the series in the hierarchy and are treated distinctly.	The ``Guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package in R software \citep{Rforecast} is uses to select $\lambda$ for the Box-Cox transformations. For the log transformations we simply set $\lambda = 0$.

Then  we fit univariate ARIMA models for the transformed series. \verb|auto.arima()| function in \verb|forecast| package is use to choose the best model that minimises the AIC. Using the fitted models, forecasts are produced for $6$ forecast horizons for each series in the hierarchy. These forecasts are then back-transformed using equation (\ref{eq:BoxCox_back-transformation}) to scale them back into the original space. However, the back transformed forecasts will be biased \citep{guerrero1993time}.

@@

	\section{Appendix}
	%\thisfloatpagestyle{empty}
	\input{Appendix}

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL
\usepackage{floatpag}
\usepackage{lipsum}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes, caption, subcaption}
\usepackage[export]{adjustbox}

@@

\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{1}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%

@@

	\begin{figure}[H]
		\centering
		\small
		\includegraphics[width = \textwidth]{Figs/OrthVsOblq_Proj_Emp_results.pdf}
		\caption{MSE difference between base forecasts and reconciled forecasts over the replications is presented for forecast horizons $h = 1,...,6$. Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
	\end{figure}

@@

%	\begin{figure}
%		\centering
%		\begin{subfigure}[t]{0.45\textwidth}
%			\centering
%			\includegraphics[width=\linewidth]{Figs/InsampDir_1.pdf} 
%%			\label{fig:InsampDir_1}
%		\end{subfigure}
%		\hfill
%		\begin{subfigure}[t]{0.45\textwidth}
%			\centering
%			\includegraphics[width=\linewidth]{Figs/InsampDir_2.pdf} 
%%			\label{fig:InsampDir_2}
%		\end{subfigure}
%		
%		\vspace{1cm}
%		
%		\begin{subfigure}[t]{0.45\textwidth}
%			\centering
%			\includegraphics[width=\linewidth]{Figs/OrthProj.pdf} 
%%			\label{fig:OrthProj}
%		\end{subfigure}
%		\hfill
%		\begin{subfigure}[t]{0.45\textwidth}
%			\centering
%			\includegraphics[width=\linewidth]{Figs/ObliqProj.pdf} 
%%			\label{fig:ObliqProj}
%		\end{subfigure}
%		
%%		\begin{subfigure}[t]{\textwidth}
%%			\centering
%%			\includegraphics[width=\linewidth]{example-image-c.pdf} 
%%			\caption{Price regulation} \label{fig:timing3}
%%		\end{subfigure}
%		\caption{A schematic to represent orthogonal and oblique reconciliation.  Points in orange colour in top left figure represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
%	\end{figure}

	\begin{figure}

	\begin{adjustbox}{minipage=\linewidth,scale=0.7}
	\begin{subfigure}[t]{0.45\textwidth}
%		\centering
		\input{Figs/InsampDir_1} 
		%			\label{fig:InsampDir_1}
	\end{subfigure}
	\hspace{1cm}
	\begin{subfigure}[t]{0.45\textwidth}
%		\centering
		\input{Figs/InsampDir_2} 
		%			\label{fig:InsampDir_2}
	\end{subfigure}

	\vfill
%	\vspace{0.3cm}

	\begin{subfigure}[t]{0.45\textwidth}
%		\centering
		\input{Figs/OrthProj} 
		%			\label{fig:OrthProj}
	\end{subfigure}
	\hspace{1cm}
	\begin{subfigure}[t]{0.45\textwidth}
%		\centering
		\input{Figs/ObliqProj} 
		%			\label{fig:ObliqProj}
	\end{subfigure}

	%		\begin{subfigure}[t]{\textwidth}
	%			\centering
	%			\includegraphics[width=\linewidth]{example-image-c.pdf} 
	%			\caption{Price regulation} \label{fig:timing3}
	%		\end{subfigure}

	\end{adjustbox}
\caption{A schematic to represent orthogonal and oblique reconciliation.  Orange colour points in top left figure represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
\end{figure}

@@

	Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice. Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}). However, our motivation in this study is to demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.

@@

	We use ``overnight trips" as a measure of domestic tourism flow in Australia. Total ``overnight trips" in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a geographical hierarchy with $110$ total number of series and $75$ bottom level series. More information about the series of this hierarchy is given in Table \ref{table:A1} in the appendix. Data were obtained from the National Visitor Survey (NVS) which were collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more. Data form a monthly series starting from January 1998 to December 2017 which gives a total of $240$ observations per series.

	As we can see from the time plots in Figure \ref{fig:Total_TSplots}, the total overnight trips has a strong seasonal pattern. Most overnight trips seems to be happening in January which is associated with the summer season in southern hemisphere. On the other hand the least trips are happening in February perhaps due to the end of summer holidays. We could also observe a slight downward trend in total overnight trips from 2005 to 2010 and then started increasing since 2010.

	Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for some selected series from states, zones and regions of the hierarchy. While observing the series in state level, we could see that Northern Territory(NT) has a different seasonal patterns compared to the other states. Highest overnight trips to NT happens during June - August where July being the peak. Lowest trips happens during December - February. This is perhaps Australians prefer to visit North of Australia during its dry season rather than in wet season. This pattern also reflect in zones and regions associated to NT as well as regions in north Queensland. All other states and their associated zones and regions show peak overnight trips in January.

	Further we noticed that the signal-to-noise ratio decreases with the level of disaggregation of the hierarchy. We can see much noisier series in regional and zone levels whereas the noise is comparatively stabilised in the upper levels. We have also observed that the overnight trips to `Adelaide Hills' has an anomalous observation on December-2002. We replace this observation with the average overnight trips on December-2001 and December-2003 for the same destination.

	Using this data we produce $h=1$ to $h=6$ month ahead forecasts based on a rolling window approach. First a training window of $100$ observations is considered from Jan-$1998$ to Apr-$2006$ and  forecasts produce for May-$2006$ to Oct-$2006$. Then we roll the training window one month at a time where the final forecast is produced for Dec-$2017$. This leads to $140 \quad 1$-step-ahead, $139 \quad 2$-step-ahead through $135 \quad 6$-step-ahead forecasts left for evaluation.

	\begin{figure}
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplots.pdf}
		\caption{Total overnight trips are presented in log scale. Top panel shows the time plot. Bottom left panel shows the sub-series plot for each month whereas bottom right panel shows the seasonal plot coloured by year  }\label{fig:Total_TSplots}
	\end{figure}

	\begin{figure}
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots.pdf}
		\caption{Time plot of overnight trips for some selected series from different disaggregate levels of the hierarchy. All values are presented in log scale. To avoid impact from the zero values we added a constant 1 to all observations}\label{fig:States_Zones_Regs_TSplots}
	\end{figure}

	\subsection{Base forecasts and reconciliation:}

	First we transform each series in the hierarchy to stabilise any variations in the data. We use two types of transformation, namely, log transformation and more general Box-Cox transformation. Equation (\ref{eq:BoxCox_transformation}) gives the mathematical formula for these transformations. A constant is added to each series to avoid the impact of zero observations when taking log transformations. We note here that the two transformations were applied separately to the series in the hierarchy and treated distinctly.

	\begin{equation} \label{eq:BoxCox_transformation}
	x_t = 
	\begin{cases} 
	\log(y_t) & \text{if log transformation, $\lambda = 0$} \\
	\frac{y_t^\lambda - 1}{\lambda}  & \text{if Box-Cox transformation, $\lambda \ne 0$} 
	\end{cases}
	\end{equation}

	The ``Guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package in R software \citep{Rforecast} is use to select optimal $\lambda$ for Box-Cox transformation. For log transformation we simply choose $\lambda = 0$. Then  we fit univariate ARIMA models for the transformed series. \verb|auto.arima()| function in \verb|forecast| package is use to choose the best model that minimises the AIC. Using the fitted models, forecasts are produced for $6$ forecast horizons for each series in the hierarchy. These forecasts are then back-transformed using equation (\ref{eq:BoxCox_back-transformation}) to scale them back into the original space. However, the back transformed forecasts will be biased \citep{guerrero1993time}.

@@

	\section{Appendix}
	\thisfloatpagestyle{empty}
	\input{Appendix}
